Analyzing Student Use of Spacing and Interleaving Strategies in Interactions with GenAI-Powered Chatbots in Programming Courses

### 2024-11-08 CSEDU2025/Paper.tex
update paper

\author{\authorname{Rodrigo Prestes Machado\sup{1}\orcidAuthor{0000-0003-0428-6387},
Carlos Alario Hoyos\sup{2}\orcidAuthor{0000-0002-3082-0814},
Patricia Callejo Pinardo\sup{2}\orcidAuthor{0000-0001-6124-6213},
Iria Estévez-Ayres\sup{2}\orcidAuthor{0000-0002-1047-5398},
Carlos Delgado Kloos\sup{2}\orcidAuthor{0000-0003-4093-3705}}
\affiliation{\sup{1}Department of Informatics, Instituto Federal de Educação,
Ciência e Tecnologia, Porto Alegre, Brazil}
\affiliation{\sup{2}Department of Telematics Engineering, Universidad Carlos III
de Madrid, Leganés (Madrid), Spain}
\email{\ rodrigo.prestes@poa.ifrs.edu.br, \{calario,pcallejo, ayres,cdk\}@it.uc3m.es}
}

@@

\abstract{
The aim of this study is to analyze the interactions of programming students
with a chatbot powered by OpenAI's GPT-3.5, enhanced with the Retrieval
Augmented Generation (RAG) technique, within the context of a Java programming
course. The study investigates how students use the chatbot while employing
two metacognitive strategies: interleaving and spacing. By analyzing the logs
of student interactions with the chatbot, the methodology involved
classifying and categorizing student prompts into eight distinct types. The
findings reveal that, while most interactions focus on active learning
strategies, students show limited conscious application of study strategies such
as interleaving and spacing. The study highlights the need for more
comprehensive guidance on the strategic use of AI tools to enhance learning
outcomes.
}

@@

The study conducted by \cite{chan23} revealed that both undergraduate and
postgraduate students have positive attitudes towards the use of GenAI.
Furthermore, a systematic review organized by \cite{Lo24} demonstrated that
students can effectively learn from ChatGPT, resulting in improved comprehension
and academic achievement \citep{Callejo24}. Furthermore, it was observed that
ChatGPT allows students to regulate their learning pace \citep{Baha24} and can
potentially support self-regulated learning, particularly for students with
prior technical and disciplinary knowledge \citep{Xia23}.

However, researchers have also expressed concerns about the impact of these
tools on students. The systematic review by \cite{Murillo23} indicated that the
use of ChatGPT could lead to overreliance on the tool. \cite{chan23} noted that
overdependence on ChatGPT could lead to a decrease in critical thinking, as
students can make decisions based solely on the information provided by the tool.
As a potential consequence, \cite{Bastani24} observed in a study that when
programming students lost access to ChatGPT-4, those who had previously relied
on it saw their performance drop by 17\%. In contrast, students who had never
used the tool were unaffected and outperformed their peers.

@@

Regardless of teachers' preferences or beliefs, preliminary surveys conducted
by \cite{Dickey24} indicate that more than 54,5\% of students are already using
GenAI for homework, likely due to their perception of this technology as
advantageous and intuitive \citep{Boudouaia24}. All of these studies highlight
the need to increase the understanding of how students interact with these tools
and how they can be used to improve learning, as emphasized \cite{Lo24}.

In response to the growing need for deeper insight into the use of GenAI tools
in educational settings, this study aims to help address this gap by analyzing
the interactions between students in a Java programming course and an
educational bot powered by OpenAI gpt-3.5, enhanced with the
Retrieval-Augmented Generation (RAG) technique. Specifically, it focuses on
examining these interactions within the context of two metacognitive strategies:
spacing and interleaving. To achieve this objective, we formulate three research
questions:

\begin{itemize}
  \item RQ1 - What distribution patterns emerged in the classified student
  interaction prompts with the educational chatbot?
  \item RQ2 - Was there spacing between student prompts? Which category led to
  the most rapid and consistent interactions with the bot?
  \item RQ3 - Do students' interactions with the bot alternate between study
  topics to suggest interleaving?
\end{itemize}

% What is its main limitation?

@@

\begin{table*}[htbp]
  \caption{Categories - adapted from \cite{Ghimire24}}
  \begin{center}
    \renewcommand{\arraystretch}{1.6} % Increase the spacing between rows
    \begin{tabular}{p{4cm} p{12cm}} % Remove vertical bars
      \hline
      \textbf{Category} & \textbf{Description} \\
      \hline
      Debugging Help (DH) & Prompts that seek help to identify, fix errors, or understand the provided code snippet. \\
      Conceptual Question (CQ) & Prompts that are more about understanding concepts than specific code. \\
      Student Correction (SC) & Prompts where the student corrects the bot. \\
      Code Snippet  (CS) & Prompts that ask for a specific part of the code, like a function or a segment. \\
      Complete Solution (CSO) & Prompts that request an entire solution or a complete code snippet. \\
      Multiple Question (MQ) & Prompts where the user wants to solve a multiple choice exercise (Quiz). \\
      Language Change (LC) & Prompts that request a change of idiom. \\
      Uncategorized (U) & Prompts that do not fit into any of the above categories. \\
      \hline
    \end{tabular}
    \label{tab:categories}
  \end{center}
\end{table*}

@@

Given that generative AI often produces highly accurate and automatic responses
\citep{Puryear22}, it is essential that students use these tools within an
active learning process to enhance their learning outcomes. This active
learning process can be further understood through the lens of metacognition,
which focuses on awareness of one's mental processes. \cite{flavell79}
proposed a model of metacognitive monitoring that includes four interrelated
phenomena: Metacognitive Knowledge, Metacognitive Experience, Metacognitive
Goals, and Metacognitive Actions. These processes do not occur in isolation, but
they influence each other, altering cognitive progress over time.

@@

CharlieBot is an educational bot built on ChatGPT 3.5 and enhanced with
Retrieval-Augmented Generation (RAG) technique to improve the precision of
responses provided to students \cite{Sun24}. The RAG approach was developed
using materials from a MOOC, including text, exercises, video transcripts, and
other resources.

@@

In the categorization phase, the students' messages were manually classified
into eight distinct categories for analysis, representing different types of
prompt that students use when interacting with the bot. Initially,
\cite{Ghimire24} proposed four categories: Debugging Help (DH), Conceptual
Question (CQ), Code Snippet (CS), and Complete Solution (CSO). However, the data
collected indicated the need for additional categories, leading to the inclusion
of four more: Multiple Question (MQ), Student Corrections (SC), Language Change
(LC), and Uncategorized (U). In this study, students were free to use the bot as
they wanted, which contributed to the emergence of these additional categories.
Table \ref{tab:categories} presents these categories along with their respective
descriptions. To facilitate the analysis of interleaving, the prompt topics were
also categorized according to the course subjects, which are: (1) Java, (2)
Object Orientation, (3) Testing, (4) Recursion, (5) Data Structures, and (6)
Sorting and Searching Algorithms.

@@

According to Figure \ref{fig:graph1} messages classified as
Conceptual Question account for 35.8\% of the total. Sequences of Conceptual
Questions often start from a practical perspective of a given code, as
illustrated in conversation 4 of Figure \ref{fig:graph2}, which presents
examples of students' interactions with the bot. In other cases, the
conversation consists entirely of messages classified as Conceptual Question,
such as in conversation 15 of Figure \ref{fig:graph2}.

@@

Requests for the bot to generate a Code Snippet or Complete Solution accounted
for 8.2\% of student messages. These prompts reflected a desire for more
direct answers; however, it was observed that, after receiving these solutions,
many students transitioned to a more active approach in seeking to understand
the code or the underlying concepts. Thus, it can be inferred that the prompts
within the Code Snippet or Complete Solution category were often used as a
starting point for a more in-depth study.

Student corrections to bot responses accounted for 4.2\% of the interactions.
In most cases, these corrections occurred when the student already had the
correct answer to an exercise and identified an error in the bot response, as
illustrated in conversation 2 in Figure \ref{fig:graph2}. These corrections
highlight that, although the bot provides quick feedback, it is not always
accurate.

Figure \ref{fig:graph1} also indicates that approximately 5.8\% of the prompts
written by students were classified as Uncategorized. These messages include
expressions of gratitude toward the bot, such as a simple '\textit{thanks}',
contextual statements like '\textit{I'm reviewing object orientation}', as well
as requests for additional exercises and summaries. Depending on the type of
investigation, there is opportunity for these messages to be further subdivided
into new categories.

Finally, 1.3\% of the messages were classified as Language Change. These prompts
were typically requests for the bot to switch languages, as seen in conversation
9 in Figure \ref{fig:graph2}.

@@

About the second part of the second research question: \textit{RQ2 - Which
category led to the most rapid and consistent interactions with the bot?}

When a student requests a code snippet (CS), it is generally predictable that
they will resume interaction with the bot within a short period of time, as
indicated by the mean (1.26) and standard deviation (1.74) of the Code Snippet
category in Table \ref{tab:averages}. This result is noteworthy because,
although some requests are simple and lead to quick responses, others may be
more complex and would require more time for reflection. However, the low
average response time and minimal variability may indicate that students adopt a
more passive learning posture when requesting the bot to generate small pieces
of code.

Despite some occasional variation (3.54), prompts classified as Uncategorized
exhibit a relatively low average time (1.65) for students to resume interaction
with the bot. This variation occurs, in part, due to situations where students
end the conversation with an uncategorized message, such as a simple
\textit{'thanks'} but later choose to resume the interaction.

When a student requests the bot to change the language (LC) in a response, the
new interaction happens quickly (1.89) with little variation in response time
(3.28), meaning it is predictable that the student will continue interacting.

Although still below the overall average, students take a moderate amount of
time (2.65) to resume interaction with the bot after requesting the solution to
a multiple-choice question (MQ). The variation (6.10) suggests that some
responses may lead to a slower follow-up interaction, possibly indicating a
moment of deeper reflection on the part of the students. However, since both the
mean and standard deviation are below the overall average, this could indicate
a more passive behavior, as students obtain ready-made answers from the bot.

The average time for students to resume interaction in the correction category
(SC) is close to the overall average (3.17), although the high standard
deviation (7.33) indicates significant variation. In some cases, students are
already familiar with the answer and only seek a quick correction from the bot;
in others, they detect flaws in the bot's responses and need to carefully
examine the subsequent answer to identify potential errors, which suggests a
more active behavior.

@@

Conceptual questions (CQ) generally result in a high average time (5.41) for
students to re-engage with the bot. Moreover, the high standard deviation
(10.54) indicates an unpredictable variation in response times. This
unpredictability may be attributed to the fact that, in some cases, the
complexity of the question and answer demands more reflection time from the
student, whereas in others, lesser complexity allows for a quicker interaction
with the bot.

Finally, a message classified as a Complete Solution request (SCO) exhibits the
longest average time (6.55) for students to resume interaction with the bot.
Additionally, the high standard deviation (10.14) highlights significant
unpredictability in response time. After requesting a complete solution,
students tend to take longer to return, due to the complexity of the problems
involved, such as the implementation of sorting algorithms like Heapsort. Table
\ref{tab:averages} presents the means and standard deviations for each
category.

@@

About the third research question: \textit{RQ3 - Do students' interactions with
the bot alternate between study topics to suggest interleaving?}

@@

In conversations with the bot that did not include spacing (66.7\% of the total
conversations), approximately 19.2\% of the messages resulted in a change of
topic. Qualitative analysis of what led to this interweaving indicates that
part of it was due to students' requests for assistance in solving exercises
from different topics, suggesting a less active learning approach, as the time
interval for this type of interaction tends to be shorter than average.
Additionally, some instances of interweaving were observed after a prolonged
period of 20 to 50 minutes, still below the 60-minute threshold established as
the cutoff for considering spacing.

In interactions with the bot that included spacing (33.3\% of the total
conversations), approximately 31.4\% of the messages switched topics.
Qualitative analysis of these interactions reveals that a significant portion
of this interweaving was caused by spacing. In other words, some students use
the bot for quick consultations, asking a question and then returning hours
later with another question on a different subject.

@@

The objective of this work was to analyze the interactions of Java programming
students with an educational bot developed using the RAG technique, employing
two metacognitive study strategies: spacing and interleaving.

The theory of metacognition, along with the classification of student actions,
proved effective in understanding and revealing how students utilize the bot.
The results showed that most messages fall into the categories of Conceptual
Questions and Debugging Help, both known for promoting slower engagement and
potentially fostering more active learning. However, the results also indicated
that students' use of study strategies such as spacing and interleaving remains
limited, from which we can conclude that encouraging students to apply these
strategies more intentionally could enhance their learning while using GenAI.

>>>>

\author{\authorname{Rodrigo Prestes Machado\sup{1}\orcidAuthor{0000-0003-0428-6387},
Carlos Alario-Hoyos\sup{2}\orcidAuthor{0000-0002-3082-0814},
Patricia Callejo\sup{2}\orcidAuthor{0000-0001-6124-6213},
Iria Estévez-Ayres\sup{2}\orcidAuthor{0000-0002-1047-5398},
Carlos Delgado Kloos\sup{2}\orcidAuthor{0000-0003-4093-3705}}
\affiliation{\sup{1}Department of Informatics, Instituto Federal de Educação,
Ciência e Tecnologia, Porto Alegre, Brazil}
\affiliation{\sup{2}Department of Telematics Engineering, Universidad Carlos III
de Madrid, Leganés (Madrid), Spain}
\email{\ rodrigo.prestes@poa.ifrs.edu.br, \{calario, pcallejo, ayres, cdk\}@it.uc3m.es}
}

@@

\abstract{
The aim of this study is to analyze the interactions of programming students
with a chatbot powered by OpenAI's GPT-3.5, enhanced with the Retrieval
Augmented Generation (RAG) technique, within the context of a Java programming
course. The study investigates how students use the chatbot while employing
two metacognitive strategies: interleaving and spacing. The methodology involved
classifying and categorizing the students' interaction prompts with the chatbot
into eight distinct categories. The findings reveal that, while most
interactions focus on active learning strategies, students demonstrate limited
conscious application of metacognitive strategies. The study highlights the need
for more comprehensive guidance on the strategic use of AI tools to enhance
learning outcomes.
}

@@

The study conducted by \cite{chan23} revealed that both undergraduate and
postgraduate students have positive attitudes towards the use of GenAI.
A systematic review organized by \cite{Lo24} demonstrated that students can
effectively learn from ChatGPT, resulting in improved comprehension and academic
achievement \citep{Callejo24}. Furthermore, it was observed that ChatGPT may
allow students to regulate their learning pace \citep{Baha24} and can
potentially support self-regulated learning, particularly for students with
prior technical and disciplinary knowledge \citep{Xia23}.

However, researchers have also expressed concerns about the impact of these
tools on students. The systematic review by \cite{Murillo23} indicated that the
use of ChatGPT could lead to overreliance on the tool. \cite{chan23} noted that
overdependence on ChatGPT could lead to a decrease in critical thinking, as
students can make decisions based solely on the information provided by the
tool. As a potential consequence, \cite{Bastani24} observed in a study that when
programming students lost access to ChatGPT, those who had previously relied
on it saw their performance drop by 17\%. In contrast, students who had never
used the tool were unaffected and outperformed their peers.

@@

Regardless of teachers' preferences or beliefs, preliminary surveys conducted
by \cite{Dickey24} indicate that more than 54.5\% of students are already using
GenAI for homework, likely due to their perception of this technology as
advantageous and intuitive \citep{Boudouaia24}. All of these studies highlight
the need to increase the understanding of how students interact with these tools
and how they can be used to improve learning, as emphasized by \cite{Lo24}.

In response to the growing need for deeper insight into the use of GenAI tools
in educational settings, this study aims to help address this gap by analyzing
the interactions between students in a Java programming course and an
educational chatbot powered by OpenAI gpt-3.5, enhanced with the
Retrieval-Augmented Generation (RAG) technique. Specifically, it focuses on
examining these interactions within the context of two metacognitive strategies:
spacing and interleaving. To achieve this objective, we formulate three research
questions:

\begin{itemize}
  \item RQ1 - What distribution patterns emerged in the classified student
  interaction prompts with the educational chatbot?
  \item RQ2 - Was there spacing between student prompts? Which category led to
  the most rapid and consistent interactions with the chatbot?
  \item RQ3 - Do students' interactions with the chatbot alternate between study
  topics to suggest interleaving?
\end{itemize}

@@

\begin{table*}[htbp]
  \caption{Categories - adapted from \cite{Ghimire24}}
  \begin{center}
    \renewcommand{\arraystretch}{1.6} % Increase the spacing between rows
    \begin{tabular}{p{4cm} p{12cm}} % Remove vertical bars
      \hline
      \textbf{Category} & \textbf{Description} \\
      \hline
      Debugging Help (DH) & Prompts that seek help to identify, fix errors, or understand the provided code snippet. \\
      Conceptual Question (CQ) & Prompts that are more about understanding concepts than specific code. \\
      Student Correction (SC) & Prompts where the student corrects the chatbot. \\
      Code Snippet  (CS) & Prompts that ask for a specific part of the code, like a function or a segment. \\
      Complete Solution (CSO) & Prompts that request an entire solution or a complete code snippet. \\
      Multiple Question (MQ) & Prompts where the user wants to solve a multiple choice exercise (Quiz). \\
      Language Change (LC) & Prompts that request a change of idiom. \\
      Uncategorized (U) & Prompts that do not fit into any of the above categories. \\
      \hline
    \end{tabular}
    \label{tab:categories}
  \end{center}
\end{table*}

@@

Given that GenAI often produces highly accurate and automatic responses
\citep{Puryear22}, it is essential that students use these tools within an
active learning process to enhance their learning outcomes. This active
learning process can be further understood through the lens of metacognition,
which focuses on awareness of one's mental processes. \cite{flavell79}
proposed a model of metacognitive monitoring that includes four interrelated
phenomena: Metacognitive Knowledge, Metacognitive Experience, Metacognitive
Goals, and Metacognitive Actions. These processes do not occur in isolation, but
they influence each other, altering cognitive progress over time.

@@

CharlieBot is an educational chatbot built on ChatGPT 3.5 and enhanced with
Retrieval-Augmented Generation (RAG) technique to improve the precision of
responses provided to students \cite{Sun24}. The RAG approach was developed
using materials from a MOOC, including text, exercises, video transcripts, and
other resources.

@@

In the categorization phase, the students' messages were manually classified
into eight distinct categories for analysis, representing different types of
prompt that students use when interacting with the chatbot. Initially,
\cite{Ghimire24} proposed four categories: Debugging Help (DH), Conceptual
Question (CQ), Code Snippet (CS), and Complete Solution (CSO). However, the data
collected indicated the need for additional categories, leading to the inclusion
of four more: Multiple Question (MQ), Student Corrections (SC), Language Change
(LC), and Uncategorized (U). In this study, students were free to use the
chatbot as they wanted, which contributed to the emergence of these additional
categories. Table \ref{tab:categories} presents these categories along with
their respective descriptions. To facilitate the analysis of interleaving, the
prompt topics were also categorized according to the course subjects, which are:
(1) Java, (2) Object Orientation, (3) Testing, (4) Recursion, (5) Data
Structures, and (6) Sorting and Searching Algorithms.

@@

According to Figure \ref{fig:graph1} messages classified as
Conceptual Question account for 35.8\% of the total. Sequences of Conceptual
Questions often start from a practical perspective of a given code, as
illustrated in conversation 4 of Figure \ref{fig:graph2}, which presents
examples of students' interactions with the chatbot. In other cases, the
conversation consists entirely of messages classified as Conceptual Question,
such as in conversation 15 of Figure \ref{fig:graph2}.

@@

Requests for the chatbot to generate a Code Snippet or Complete Solution accounted
for 8.2\% of student messages. These prompts reflected a desire for more
direct answers; however, it was observed that, after receiving these solutions,
many students transitioned to a more active approach in seeking to understand
the code or the underlying concepts. Thus, it can be inferred that the prompts
within the Code Snippet or Complete Solution category were often used as a
starting point for a more in-depth study.

Student corrections to chatbot responses accounted for 4.2\% of the interactions.
In most cases, these corrections occurred when the student already had the
correct answer to an exercise and identified an error in the chatbot response,
as illustrated in conversation 2 in Figure \ref{fig:graph2}. These corrections
highlight that, although the chatbot provides quick feedback, it is not always
accurate.

Figure \ref{fig:graph1} also indicates that approximately 5.8\% of the prompts
written by students were classified as Uncategorized. These messages include
expressions of gratitude toward the chatbot, such as a simple '\textit{thanks}',
contextual statements like '\textit{I'm reviewing object orientation}', as well
as requests for additional exercises and summaries. Depending on the type of
investigation, there is opportunity for these messages to be further subdivided
into new categories.

Finally, 1.3\% of the messages were classified as Language Change. These prompts
were typically requests for the chatbot to switch languages, as seen in
conversation 9 in Figure \ref{fig:graph2}.

@@

About the second part of the second research question: \textit{RQ2 - Which
category led to the most rapid and consistent interactions with the chatbot?}

When a student requests a code snippet (CS), it is generally predictable that
they will resume interaction with the chatbot within a short period of time, as
indicated by the mean (1.26) and standard deviation (1.74) of the Code Snippet
category in Table \ref{tab:averages}. This result is noteworthy because,
although some requests are simple and lead to quick responses, others may be
more complex and would require more time for reflection. However, the low
average response time and minimal variability may indicate that students adopt a
more passive learning posture when requesting the chatbot to generate small pieces
of code.

Despite some occasional variation (3.54), prompts classified as Uncategorized
exhibit a relatively low average time (1.65) for students to resume interaction
with the chatbot. This variation occurs, in part, due to situations where students
end the conversation with an uncategorized message, such as a simple
\textit{'thanks'} but later choose to resume the interaction.

When a student requests the chatbot to change the language (LC) in a response, the
new interaction happens quickly (1.89) with little variation in response time
(3.28), meaning it is predictable that the student will continue interacting.

Although still below the overall average, students take a moderate amount of
time (2.65) to resume interaction with the chatbot after requesting the solution to
a multiple-choice question (MQ). The variation (6.10) suggests that some
responses may lead to a slower follow-up interaction, possibly indicating a
moment of deeper reflection on the part of the students. However, since both the
mean and standard deviation are below the overall average, this could indicate
a more passive behavior, as students obtain ready-made answers from the chatbot.

The average time for students to resume interaction in the correction category
(SC) is close to the overall average (3.17), although the high standard
deviation (7.33) indicates significant variation. In some cases, students are
already familiar with the answer and only seek a quick correction from the chatbot;
in others, they detect flaws in the chatbot's responses and need to carefully
examine the subsequent answer to identify potential errors, which suggests a
more active behavior.

@@

Conceptual questions (CQ) generally result in a high average time (5.41) for
students to re-engage with the chatbot. Moreover, the high standard deviation
(10.54) indicates an unpredictable variation in response times. This
unpredictability may be attributed to the fact that, in some cases, the
complexity of the question and answer demands more reflection time from the
student, whereas in others, lesser complexity allows for a quicker interaction
with the chatbot.

Finally, a message classified as a Complete Solution request (SCO) exhibits the
longest average time (6.55) for students to resume interaction with the chatbot.
Additionally, the high standard deviation (10.14) highlights significant
unpredictability in response time. After requesting a complete solution,
students tend to take longer to return, due to the complexity of the problems
involved, such as the implementation of sorting algorithms like Heapsort. Table
\ref{tab:averages} presents the means and standard deviations for each
category.

@@

About the third research question: \textit{RQ3 - Do students' interactions with
the chatbot alternate between study topics to suggest interleaving?}

@@

In conversations with the chatbot that did not include spacing (66.7\% of the total
conversations), approximately 19.2\% of the messages resulted in a change of
topic. Qualitative analysis of what led to this interweaving indicates that
part of it was due to students' requests for assistance in solving exercises
from different topics, suggesting a less active learning approach, as the time
interval for this type of interaction tends to be shorter than average.
Additionally, some instances of interweaving were observed after a prolonged
period of 20 to 50 minutes, still below the 60-minute threshold established as
the cutoff for considering spacing.

In interactions with the chatbot that included spacing (33.3\% of the total
conversations), approximately 31.4\% of the messages switched topics.
Qualitative analysis of these interactions reveals that a significant portion
of this interweaving was caused by spacing. In other words, some students use
the chatbot for quick consultations, asking a question and then returning hours
later with another question on a different subject.

@@

The objective of this work was to analyze the interactions of Java programming
students with an educational chatbot developed using the RAG technique, employing
two metacognitive study strategies: spacing and interleaving.

The theory of metacognition, along with the classification of student actions,
proved effective in understanding and revealing how students utilize the chatbot.
The results showed that most messages fall into the categories of Conceptual
Questions and Debugging Help, both known for promoting slower engagement and
potentially fostering more active learning. However, the results also indicated
that students' use of study strategies such as spacing and interleaving remains
limited, from which we can conclude that encouraging students to apply these
strategies more intentionally could enhance their learning while using GenAI.
